Supplemental material

### 2024-04-24 paper/resp_referee.qmd
update plots + articles

@@

@@

@@

The modelled of the input time series is now describe more precisely in section 2 (previous section 1). $TC_t$ is here considered as deterministic

@@

@@

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed. Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift. I can be explain that the bi*

@@

In local polynomial smoothing, the notion of bias is associated to the approximation error of the smoothed series by a polynomial degree of order $d$.
It can thus be writer as

@@

@@

@@

> The author simulates time series of length 60 years to illustrate the methodology at the end of the series.
It may be worth considering (in addition) shorter series. 
Another thought is that the ARIMA model being used to extend the series appears to be modeled using the full series; what if the ARIMA model used to extend the series was instead estimated using just a short span toward the end of the series?
*Indeed it is in general not relevant to identify an ARIMA model on a monthly time series of length 60 years.*
In our case, since the same data generation process remains the same, it could be relevant and leads to better results in terms of delay to detect turning points (in supplement materials, a plot is added comparing the results with different spans to identify/estimate the ARIMA model).
However, on the main text, we now only used 12 years to identify the ARIMA model, to be closer to what would be done on real series.

@@

> Some of the important results appear in the tables and figures, but the accompanying discussion in the text should still be fleshed out more.  In addition, in Figures 2-4 and 6-7 (and the figures in the supplement), the lines can be distinguished by color, but it may be helpful to find some way to keep them distinguishable without the benefit of color.  It might be the case that there is too much information to display neatly in some of these.

@@

Other (non-exhaustive) [only remarks that require a response]
- P2 L8:  “X-13ARIMA seasonal adjustment method” -- The software is officially X-13ARIMA-SEATS, but the seasonal adjustment method itself is X-11 (applies to subsequent occurrences as well)

@@

- P2 L29:  “good properties” -- This could be less vague.

- P7 L58:  There is a $q$ introduced here via “$w_t^q$ for $t>q$” that shows up later as well, but  itself does not appear to be properly defined otherwise.

@@

- P9:  Author lists a number of quality criteria in Table 1.  It may be obvious for some of these, but it would be helpful to the reader to indicate whether lower values or higher values are preferable for each, either in the table or in the accompanying exposition.

@@

- P11 L22:  “$2h+1 \geq d+1$” -- Why not just say $2h\geq d$?

@@

- P14 L33:  More exposition wrt Table 2 may be helpful, as there is a fair amount of information to digest.

@@

- P14 L45:  What is the rationale for this combined measure $EQM_w=A_w + S_w + T_w + R_w$?  Looking at the expressions for these four from Table 1, it is apparent that $A_w$ and $T_w$ sum up (the two have the same integrand, and the resulting sum is the integral from 0 to $\pi$), and same goes for $S_w$ and $R_w$.  
And it should probably be explicitly stated what $EQM_w$ stands for prior to introducing it in the table.

@@

- P19 L15:  “January 1960 and December 2020” -- As noted previously, is it worth considering an additional scenario with (simulated) series of shorter length?

@@

@@

@@

@@

@@

>>>>

*The final filter used in X-11 is much longer than one year.*
*The series are thus just partially extended (and asymmetric filters are still used): this avoid problems associated to long horizon forecasting (outliers/shifts).*
*This was clarified in the text.*

@@

*More explanation are added to this section*

@@

*All the section was rewritten to be clearer*

@@

*The modelled of the input time series is now describe more precisely in section 2 (previous section 1). $TC_t$ is here considered as deterministic*

@@

*The definition was clarified.*
*In this paper we focus on turning points associated to business-cycles: they are defined as changepoints.*
*However, the method usually used to detect turning point makes no difference between regular points at which the slope of the trend changes sign and changepoints.*
*It is then possible to detect "false turning points" (undesirable ripples): that's why in the simulation we only focus on the simulated turning points and in real data application we look at turning points which are officially dated (for the US by the NBER).*

@@

*The notation is simplified and unified and the equations/notations clarified.*
*The matrix $D$ is needed to see the equivalence with symmetric filter/DAF (clarified in the text).*

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methodes (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher;*

@@

*In local polynomial smoothing, the notion of bias is associated to the approximation error of the smoothed series by a polynomial degree of order $d$.*
*If the moving average $\theta$ preserve a polynomial of degree $d$, the bias at the date $t$ is then:*
$$
\mathbb E[\hat \mu(t)] - \mu(t)=\sum_{j=d+1}^{+\infty}\frac{\mu^{(j)}(t)}{j!}\sum_{k=-h}^k\theta_k k^j
$$
*It is then not directly related to the phase shift.*

@@

*The term "undersirable oscillations" was removed*

@@

*Reference are added and the goal of the paper was clarified in new section 2 (previous section 1)*

@@

> The author simulates time series of length 60 years to illustrate the methodology at the end of the series.
It may be worth considering (in addition) shorter series. 
Another thought is that the ARIMA model being used to extend the series appears to be modeled using the full series; what if the ARIMA model used to extend the series was instead estimated using just a short span toward the end of the series?

*Indeed it is in general not relevant to identify an ARIMA model on a monthly time series of length 60 years.*
*In our case, since the same data generation process remains the same, it could be relevant and leads to better results in terms of delay to detect turning points (in supplement materials, a plot is added comparing the results with different spans to identify/estimate the ARIMA model).*
*However, on the main text, we now only used 12 years to identify the ARIMA model, to be closer to what would be done on real series.*
*Since other methods are local, it is not a problem to have long time series.*

@@

> Some of the important results appear in the tables and figures, but the accompanying discussion in the text should still be fleshed out more.

> In addition, in Figures 2-4 and 6-7 (and the figures in the supplement), the lines can be distinguished by color, but it may be helpful to find some way to keep them distinguishable without the benefit of color.  
It might be the case that there is too much information to display neatly in some of these.

*Figures are now black and white a scaled gray legend.*
*In some of them, there are indeed a lot of information with several labels, but the goal is not to be able to read all the details of all the lines but to see the general behavior of the filters (for example if the implicit forecasts seem relevant or not)*

@@

*We try to clarify in the section associated to the proposed methods: all the functions mentionned are already in rjd3filters.*
*The local parametrisation is not directly in the package but can be easily implemented (especially because the code is available): the variance estimator is in the package but not the moving-averages associated to slope/concavity estimators (which can be easily derived)*

Other (non-exhaustive) [only remarks that require a response]

> - P2 L8:  “X-13ARIMA seasonal adjustment method” -- The software is officially X-13ARIMA-SEATS, but the seasonal adjustment method itself is X-11 (applies to subsequent occurrences as well)

@@

> - P2 L29:  “good properties” -- This could be less vague.

*TODO*

> - P7 L58:  There is a $q$ introduced here via “$w_t^q$ for $t>q$” that shows up later as well, but  itself does not appear to be properly defined otherwise.

@@

> - P9:  Author lists a number of quality criteria in Table 1.  It may be obvious for some of these, but it would be helpful to the reader to indicate whether lower values or higher values are preferable for each, either in the table or in the accompanying exposition.

@@

> - P11 L22:  “$2h+1 \geq d+1$” -- Why not just say $2h\geq d$?

@@

> - P14 L33:  More exposition wrt Table 2 may be helpful, as there is a fair amount of information to digest.

@@

> - P14 L45:  What is the rationale for this combined measure $EQM_w=A_w + S_w + T_w + R_w$?  
> Looking at the expressions for these four from Table 1, it is apparent that $A_w$ and $T_w$ sum up (the two have the same integrand, and the resulting sum is the integral from 0 to $\pi$), and same goes for $S_w$ and $R_w$.  
> And it should probably be explicitly stated what $EQM_w$ stands for prior to introducing it in the table.

@@

> - P19 L15:  “January 1960 and December 2020” -- As noted previously, is it worth considering an additional scenario with (simulated) series of shorter length?

@@

*Quarterly series with simulated data are added in supplemental material, a new section was added to discuss the use of the methods with different periodicities*

@@

*The definition of phase-shift was clarified in*

@@

*TODO*

@@

*We try to clarify the contribution in the abtract, introduction and in the beginning of sections 2 and 3*

@@

*A new section was added with an example around Covid19 and some possible solutions for outliers*

### 2024-04-24 paper/supp_material.qmd
update plots + articles

\newpage
# Quarterly data

@@

::: {#fig-graphs-impact-span}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_lp.pdf")
```

@@

::: {#fig-graphs-impact-span}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_lp.pdf")
```
Note:

>>>>

# Quarterly data

@@

::: {#fig-nn-lp}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_lp.pdf")
```

@@

::: {#fig-nn-localparam}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_localparam.pdf")
```
Note: nearest bandwidth moving average are used to estimate slope and concavity.
We thus do not distinguish local parametrisation and final local parametrisation which asumptions might not be plausible.
Indeed, using the same framework as for fixed bandwidth, the final local parametrisation for real time estimates would implie modelling a polynomial of degree 2 or 3 other 25 months (which doesn't seem plausible).
